\Title

### 2019-12-19 manuscript/manuscript.tex
Continue writing manuscript

The depth of the point sources can be chosen following different criteria.
The most simple option is to locate all point sources at the same depth, which we will
call \emph{constant depth} in the future.
It could introduce some artifacts, like

>>>>

The depth of the point sources can be chosen following different criteria.
Deep sources generate low frequencies, while shallow ones generate high frequencies
(cite).
The most simple option is to locate all point sources at the same depth, which we will
call \emph{constant depth} in the future.
If the measurement where taken at significantly different altitudes, the elevated
computation points will be more distant to the sources than the lower ones.
This may create problems on reproducing high frequencies on the elevated points.

One possible solution is to locate each source bellow its corresponding observation
point or block-median point at a constant \emph{relative depth} from it.
The sources won't be all at the same depth, but they will all be at the same distance
from their corresponding observation point or block-median point.
It worth mention that this approach could not be applied to \emph{grid sources}.

In case our survey presents heavily clustered data points, we may want to reduce the
depth of the sources bellow that region in order to reproduce the high frequencies
measured by these clustered observation points.
We can propose a \emph{variable relative depth} approach that locates each point source
to a depth proportional to the mean distance to its $k$ nearest source neighbours
\citep{cordell1992, guspi2004, guspi2009}.
We propose to add a static shift to the computed depth in order to prevent very shallow
sources in case the mean distance to the $k$ nearest neighbours is too small.
In summary, the depth of the sources can be set as follows:

\begin{equation}
    \textrm{depth} =
        \textrm{depth_factor} \textrm{mean_distance} + \textrm{static_shift}
\end{equation}

\noindent where the $\textrm{depth_factor}$ and the $\textrm{static_shift}$ are
parameters and the $\textrm{mean_distance}$ is the mean distance to the $k$ nearest
source neighbours.

The combination of the three source layouts with the three strategies to define the
depth of the sources define seven different source distributions
(see Table~\ref{tab:source-distributions}).
The \emph{grid sources} is only compatible with the \emph{constant depth} scheme.
